Education and the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-14 GEMDataSource.Rmd
Update GEMDataSource.Rmd

#### Causal Chain

@@

Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at country-level in its NES Survey. Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative."

@@

@@

# Library required packages repmis, ridy, reshape2, plyr, WDI, and stargazer packages
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(WDI)
library(stargazer)

@@

@@

#### Summary

The impact of cultural factors in education on the rate of entrepreneurship in a given country is an important and under-researched topic that should be considered by policymakers constructing public education budgets. Through this project, we hope to encourage the consideration of these cultural factors by providing a qualitative and quantitative method for understanding the impact of these factors. Although several challenges remain to compiling the indexes discussed in this report, we are confident we can produce a helpful framework for examining and understanding these factors.

>>>>

#### Estimation Strategy

##### Causal Chain

@@

@@

##### Regressions

@@

# Library required packages repmis, ridy, reshape2, plyr and WDI packages
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(WDI)

@@

# Library Stargazer for regression output tables
library(stargazer)

@@

#### Outlook

Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at country-level in its NES Survey. Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self-esteem a given education system is.

We may also want to quantify how individualistic or group-oriented an average student is by the end of compulsory education, as the literature holds social inclusion as an explanatory factor for self-esteem. We will use OECD PISA data on "the sense of belonging" for this.

Next steps will also include looking more thoroughly into control variables. To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.
